### 2025-01-24 skripsi/chapter1.tex
update outline to be like the UPI format with chapter abstracts

% !TEX root = ./skripsi.tex
\chapter{INTRODUCTION}
\section{Background}\label{sec:background}
% TODO:talk about mathematical models and governing equations here instead. PDEs can be talked later as a subset of governing equations
\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes. This is because many systems can be described by the way they change and often this can be more intuitive. As an example, think of someone heating up a large frying pan on a gas stove. To describe how the pan heats up when the center is right above the burner, one can say that the center would heat up first followed by its surroundings. Eventually the pan would not heat up any further. Also notice that the edges of the pan would always be cooler than the center. However, once a more complex setup is introduced such as an uneven heat source or more complex materials with different heat rates of transferring heat it becomes much harder to describe how the pan heats up. A more useful way to describe the system is using the heat equation. For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \lccref{eq:heat_equation}.
\begin{equation} \label{eq:heat_equation}
    \pdv{u}{t}=\divergence{\left(\alpha \gradient u\right)}
\end{equation}
The divergence operator \(\divergence \) denotes sum of all first spatial derivatives. In three dimensions this is \(\divergence=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}\). And the gradient operator \(\gradient \) is the vector of all first spatial derivatives which in three dimensions is \(\gradient{f} = {\begin{bmatrix}\pdv{f}{x_1} & \pdv{f}{x_2} & \pdv{f}{x_3}\end{bmatrix}}^{\intercal}\). This equation says that the rate at which the temperature changes in time \(\pdv{u}{t}\) is proportional to how different the differences in temperature of a spot in the pan with its surroundings \(\laplacian{u}\) multiplied with thermal diffusivity parameter \(\alpha \). One example of an insight this gives is that given a homogeneous material (\(\alpha \) is constant) and the stove outputs heat at a constant rate the temperature will no longer change for a particular point once the temperature difference is constant. In other words once the function \(u\left(\vb{x},t\right)\) at some time \(t > 0 \) approaches a linear function in space, the temperature at all spots will no longer change in time. Mathematically this is because the time derivative is zero if the second spatial derivatives are also zero. Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting. This insight is an example of why PDEs are useful.

@@

\section{Outline}
\noindent This thesis will be structured into five chapters with this chapter being the first. For further detail on the topics relevant to this study, \lccref{sec:literature_review} will discuss and summarize the related literature. The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field. In \lccref{sec:research_methodology}, we discuss the methodology that is used in this study to achieve the aims that were set in the first chapter. And then, the results of applying the research methodology are presented in \lccref{sec:results_and_discussion}. In this section, the results are also analyzed and discussed. Finally, in \lccref{sec:conclusions_and_future_work} we draw conclusions from the results and future directions of research for the use of SVMs in operator learning with basis functions.
% \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab. Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I. Sebaiknya langsung dituliskan secara ringkas isi rincian bab-bab selanjutnya, misalnya, \textit{Setelah Pendahuluan pada Bab I ini, Bab II akan mengulas tentang ...}

>>>>

% !TEX root = ./skripsi.tex
\chapter{INTRODUCTION}\label{ch:introduction}
\section{Background}\label{sec:background}
% TODO:talk about mathematical models and governing equations here instead. PDEs can be talked later as a subset of governing equations
\noindent Partial differential equations (PDE) are a common tool widely used in the modern scientific understanding and many engineering processes. This is because many systems can be described by the way they change and often this can be more intuitive. As an example, think of someone heating up a large frying pan on a gas stove. To describe how the pan heats up when the center is right above the burner, one can say that the center would heat up first followed by its surroundings. Eventually the pan would not heat up any further. Also notice that the edges of the pan would always be cooler than the center. However, once a more complex setup is introduced such as an uneven heat source or more complex materials with different heat rates of transferring heat it becomes much harder to describe how the pan heats up. A more useful way to describe the system is using the heat equation. For a temperature function \(u\left(\vb{x},t\right)\) of spatial coordinates vector \(\vb{x}\) and time \(t\), the generalized heat equation is defined in \lccref{eq:heat_equation}.
\begin{equation} \label{eq:heat_equation}
    \pdv{u}{t}=\divergence{\left(\alpha \gradient u\right)}
\end{equation}
The divergence operator \(\divergence \) denotes sum of all first spatial derivatives. In three dimensions this is \(\divergence=\pdv{\cdot}{x_1}+\pdv{\cdot}{x_2}+\pdv{\cdot}{x_3}\). And the gradient operator \(\gradient \) is the vector of all first spatial derivatives which in three dimensions is \(\gradient{f} = {\begin{bmatrix}\pdv{f}{x_1} & \pdv{f}{x_2} & \pdv{f}{x_3}\end{bmatrix}}^{\intercal}\). This equation says that the rate at which the temperature changes in time \(\pdv{u}{t}\) is proportional to how different the differences in temperature of a spot in the pan with its surroundings \(\laplacian{u}\) multiplied with thermal diffusivity parameter \(\alpha \). One example of an insight this gives is that given a homogeneous material (\(\alpha \) is constant) and the stove outputs heat at a constant rate the temperature will no longer change for a particular point once the temperature difference is constant. In other words once the function \(u\left(\vb{x},t\right)\) at some time \(t > 0 \) approaches a linear function in space, the temperature at all spots will no longer change in time. Mathematically this is because the time derivative is zero if the second spatial derivatives are also zero. Intuitively this is because once the temperature distribution approaches linear, the current spot on the pan is outputting as much heat it is getting. This insight is an example of why PDEs are useful.

@@

\section{Outline}
\noindent This thesis will be structured into five chapters with this chapter being the first. This outline will provide a summary of each chapter. The outline is as follows:

\noindent\chref{ch:introduction}\\
\noindent This chapter begins with the background and relevant context of the problem of governing equations and their solutions. Their importance and the methods that are used to solve them are also discussed. This leads to the problem statement and goals based on said problems. The limitations and contribution are also derived from the background and context. Finally, the chapter ends with the outline that discusses structure of this thesis.

\noindent\chref{ch:literature_review}\\
\noindent For further detail on the topics relevant to this study, the second chapter will discuss and summarize the related literature. The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field. The specific components that will be covered are the Fourier transform, governing equations, and machine learning regression.

\noindent\chref{ch:research_methodology}\\
\noindent In this chapter we discuss the methodology that is used in this study to achieve the aims that were set in the first chapter. The chapter starts by explaining the steps within the research process from the problem specification to the analysis and discussion. Then the specific approach to data acquisition, literature study, and the computational model implementation are discussed. The last section of this chapter list the hardware and software tools that will be used in this study.

\noindent\chref{ch:results_and_discussion}\\
\noindent The results of applying the research methodology are presented in this chapter. This chapter starts with the data generation and retrieval results. Then, the SpectralSVR software library is development discussed from the design to the implementation and testing. The chapter then continues to the experimental scenarios the proposed model will be used. The experimental results are then presented and then discussed.

\noindent\chref{ch:conclusions_and_future_work}\\
\noindent Finally, in this chapter we draw conclusions from the results and analysis that was done in the previous chapter. Based on the analysis of weaknesses and unexplored questions, the future directions of research are also explored.
% \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab. Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I. Sebaiknya langsung dituliskan secara ringkas isi rincian bab-bab selanjutnya, misalnya, \textit{Setelah Pendahuluan pada Bab I ini, Bab II akan mengulas tentang ...}

### 2025-01-24 skripsi/chapter4.tex
update outline to be like the UPI format with chapter abstracts

% !TEX root = ./skripsi.tex
\chapter{RESULTS AND DISCUSSION}\label{sec:results_and_discussion}
\noindent This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.

@@

        # compute coefficients
        if torch.is_complex(f):
            f = to_real_coeff(f)
        coeff = self.svr.predict(f)
        # convert to complex if basis needs complex values so that the reshaping is correct
        if self.basis.coeff_dtype.is_complex:
            coeff = to_complex_coeff(coeff)

@@

\begin{figure}[H]
  \centering
  \begin{lstlisting}[language=Python]
...
    def inverse_coeff(
        self,
        u_coeff: torch.Tensor,
        loss_fn: Callable[
            [torch.Tensor, torch.Tensor], torch.Tensor
        ] = mean_squared_error,
        epochs=100,
        generator=torch.Generator().manual_seed(42),
        gain=0.05,
        **optimizer_params,
    ):
        f_shape = (u_coeff.shape[0], self.svr.sv_x.shape[1])
        complex_coeff = u_coeff.is_complex()
        original_device = u_coeff.device
        u_coeff = to_real_coeff(u_coeff.flatten(1)).to(self.svr.device)

        # inverse problem
        f_coeff_pred = (
            torch.randn(f_shape, generator=generator).to(self.svr.device) * gain
        )
        f_coeff_pred.requires_grad_()
        optim = torch.optim.Adam([f_coeff_pred], **optimizer_params)

>>>>

% !TEX root = ./skripsi.tex
\chapter{RESULTS AND DISCUSSION}\label{ch:results_and_discussion}
\noindent This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.

@@

        # compute coefficients
        if torch.is_complex(f):
            f = to_real_coeff(f)
        coeff = self.svr.predict(f)
        # convert to complex if basis needs complex
        # values so that the reshaping is correct
        if self.basis.coeff_dtype.is_complex:
            coeff = to_complex_coeff(coeff)

@@

\begin{figure}[H]
  \centering
  \begin{lstlisting}[language=Python]
...
    def inverse_coeff(
        self,
        u_coeff: torch.Tensor,
        loss_fn: Callable[
            [torch.Tensor, torch.Tensor], torch.Tensor
        ] = mean_squared_error,
        epochs=100,
        generator=torch.Generator().manual_seed(42),
        gain=0.05,
        **optimizer_params,
    ):
        f_shape = (u_coeff.shape[0], self.svr.sv_x.shape[1])
        complex_coeff = u_coeff.is_complex()
        original_device = u_coeff.device
        u_coeff = to_real_coeff(
          u_coeff.flatten(1)
        ).to(self.svr.device)

        # inverse problem
        f_coeff_pred = (
            torch.randn(
              f_shape, generator=generator
            ).to(self.svr.device) * gain
        )
        f_coeff_pred.requires_grad_()
        optim = torch.optim.Adam([f_coeff_pred], **optimizer_params)
